My Story of Applying LIME to a Random Forest Model and the Problems that Ensued

### 2019-02-26 journals/06-assessing_lime_explanations/06-assessing_lime_explanations.Rmd
updates before meeting

chosen_features %>%
  filter(set == "Set 1") %>%
  mutate(case = factor(case, levels = order)) %>%
  View()

  ggplot(aes(x = situation, y = case, fill = first)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
```

>>>>

chosen_features %>%
  filter(set == "Set 1") %>%
  mutate(case = factor(case, levels = order))
  ggplot(aes(x = situation, y = case, fill = first)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
```

### 2019-02-26 presentations/graphics group/applying lime to a random forest and the problems that ensue.Rmd
updates before meeting

---
title: "Applying LIME to a Random Forest Model and the Problems that Ensue"
author: "Katherine Goode"
date: "March 1, 2019"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

# Get Started

>>>>

---
title: "My Story of Applying LIME to a Random Forest Model and the Problems that Ensued"
author: "Katherine Goode"
date: "March 1, 2019"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

## Overview

1. Overview of LIME
2. Hamby bullet matching data
3. Applying LIME to the bullet data
4. Issues with LIME
5. Attempts at a Solution
6. Future Work
